Downward shortwave solar irradiance enhancement by clouds.

### 2024-05-24 article/article.tex
Commit 2024-05-24 11:10

\begin{itemize}
\tightlist
\item
  max value ECE relative to other works max values
\end{itemize}

Analogous to Figure\nobreakspace{}\ref{fig:relative-month-occurancies}
we have computed the distribution of the number of occurrences of ECE
events by month in
Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}. Here the
most active period is in the spring and the start of the summer (March
-- June), followed by the late fall (Septemcer and October).

\ldots\ldots.

@@

{\centering \includegraphics[width=0.5\linewidth]{../images/extremedistributions-2}

@@

\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-3}
\end{figure}

\begin{itemize}
\tightlist
\item
  SZA
\end{itemize}

@@

Created a clear sky approximation and a long term change representation
for a period of 30 years.

Identify CE events and found a trend on \ldots.. The climatology of CE
occurrences over the whole period and the magnitude of the CE events. We
estabished the occurances of extreme CE events \ldots{} The
characteristic of the duration of ``continuous'' CE events. with their
magnitude occurnacies and climatology

>>>>

Analogous to Figure\nobreakspace{}\ref{fig:relative-month-occurancies}
we have computed the distribution of the number of occurrences of ECE
events by month in
Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}. The most
active period for ECE events is in the spring and the start of the
summer (March -- June), followed by a period in the late fall (September
and October). This is probably an effect of the weather characteristics
of those periods where, there are continuous alternations between clear
sky periods and clouds.

@@

{\centering \includegraphics[width=0.5\linewidth]{../images/P-extreme-distribution-1}

@@

\caption{Distribution of ECE above clear sky threshold.}\label{fig:unnamed-chunk-3}
\end{figure}

@@

By creating a clear sky approximation of the GHI, which can represent
the long- and short-term variation of the expected clear sky GHI, we
were able to identify cases of CE events. By analysing the CE cases we
found

The climatology of CE occurrences over the whole period and

the magnitude of the CE events. We estabished the occurances of extreme
CE events \ldots{} The characteristic of the duration of ``continuous''
CE events. with their magnitude occurnacies and climatology
